%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[document]{ragged2e}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Morva Saaty} \\ \vspace{1pt}
    \small (+1)540-385-1764 $|$ \href{mailto:x@x.com}{morvasaaty@vt.edu} $|$ 
    \href{https://linkedin.com/in/morva-saaty}{\underline{linkedin.com/in/morva-saaty}} 
   % \href{https://github.com/...}{\underline{github.com/jake}}
\end{center}

%-----------EDUCATION-----------
\section{Summary}
 \justify{I am a Ph.D. student at Virginia Tech pursuing my doctoral degree in Computer Science \& Applications. I have a strong research background in Human-Computer Interaction (HCI), User Experience Design, Visual Attention, and Gamification. I am also proficient in program design and development using Python, Java, and C++. With a broad skill set covering qualitative and quantitative analysis methods, experimental research, and knowledge of multiple language programming languages, I am constantly looking for opportunities to improve, extremely passionate to broaden my research experience, and highly motivated to learn.}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Virginia Polytechnic Institute and State University}{Aug. 2020 -- Expected May. 2024}
      {Ph.D. in Computer Science and Applications - GPA: 4/4.0}{Blacksburg, VA, US}
    \resumeSubheading
      {University of Tehran}{Sep. 2016 - Dec 2018}
      {M.Sc. in Information Technology Engineering - GPA: 4/4.0}{Tehran, Iran}
    \resumeSubheading
      {University of Tehran}{Sep. 2011 - June. 2016}
      {B.Sc. in Information Technology Engineering}{Tehran, Iran}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Graduate Research Assistant}{June 2019 -- Present}
      {Virginia Polytechnic Institute and State University}{Blacksburg, VA, US}
      \resumeItemListStart
        \resumeItem{%Developed an Android mobile application to minimize disorientation in Informal Learning Environments using Java, Android Studio, and PostgreSQL to store data\\
        Designing Mobile Applications to Minimize Disorientation in Informal Learning Environments(ILE) with a focus on children by using Java, Android Studio, and PostgreSQL to store data. (Paper is accepted in IDC 2021) \\
        \underline{Methods:} Participant Observation, Experiment Design, Qualitative/Quantitative Analysis, App Development}
        \resumeItem{Exploring social experiences afforded by app/game/technology-mediated and understanding design considerations for remote recreation solutions.  \\
         \underline{Methods:} Surveys, Diaries, Focus Groups, Qualitative Analysis}
        \resumeItem{Understanding user needs and motivational factors to design and develop a location-based mobile exergame which can encourage users to do exercise for long term while engaging them in outdoors. \\
        \underline{Methods:} Social Media Analysis (NLP and Machine Learning techniques), Diaries, Focus Groups, Qualitative Analysis, Prototyping, Personas}
     %   \resumeItem{Explored ways to visualize GitHub collaboration in a classroom setting}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Graduate Research Assistant}{July. 2017 - Jan. 2019}
      {University of Tehran}{Tehran, Iran}
      \resumeItemListStart
        \resumeItem{Master's Thesis: Studying the Effect of Audio Features on Players' Visual Attention Map contributing toward a Conceptual Audio-Visual Game Attention Model for Efficient Bitrate Allocation in Cloud Gaming. - using Eye Tracking system. (Paper is submitted)  \\
        \underline{Methods:} Experiment Design, Semi-Structured Interviews, Qualitative/Quantitative Analysis}
      %  \resumeItem{Communicate with managers to set up campus computers used on campus}
       % \resumeItem{Assess and troubleshoot computer problems brought by students, faculty and staff}
        %\resumeItem{Maintain upkeep of computers, classroom equipment, and 200 printers across campus}
    \resumeItemListEnd
    


    %\resumeSubheading
     % {Artificial Intelligence Research Assistant}{May 2019 -- July 2019}
      %{Southwestern University}{Georgetown, TX}
      %\resumeItemListStart
       % \resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
        %\resumeItem{Developed a game in Java to test the generated dungeons}
        %\resumeItem{Contributed 50K+ lines of code to an established codebase via Git}
        %\resumeItem{Conducted  a human subject study to determine which video game dungeon generation technique is enjoyable}
        %\resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus}
        %\resumeItem{Presented virtually to the World Conference on Computational Intelligence}
     % \resumeItemListEnd

  \resumeSubHeadingListEnd
  
  
   %-----------Publications-----------
\section{Publications}
    \resumeSubHeadingListStart
     \resumeProjectHeading
        {\textbf{Conference Proceedings} }{}
          \resumeItemListStart
            \resumeItem{\textbf{[CHI Play 2021]} \textbf{Morva Saaty}, Derek Haqq, Devin B. Toms, Ibrahim Eltahir, and D. Scott McCrickard. "A Study on Pokémon GO: Exploring the Potential of Location-based Mobile Exergames in Connecting Players with Nature.” In Proceedings of the Annual Symposium on Computer-Human Interaction in Play, Virtual Event, Austria, 2021.}
        \resumeItemListEnd 
        \resumeItemListStart
            \resumeItem{\textbf{[CSCW 2021]} Neelma Bhatti, Lindah Kotut, Derek Haqq, Timothy L. Stelter, \textbf{Morva Saaty}, Aisling Kelliher,  and D. Scott McCrickard. “Parenting, Studying And Working At Home In A Foreign Country: How International Student Mothers In The US Use Screen Media For And With Their Young Children.”  Computer Supported Cooperative Work (CSCW), 2021.}
        \resumeItemListEnd
        \resumeItemListStart
            \resumeItem{\textbf{[IDC 2021 - Best paper honorable mention award]} Neelma Bhatti, \textbf{Morva Saaty}, and Scott McCrickard. "Designing Mobile Applications to Minimize Disorientation in Informal Learning Environments." In Interaction Design and Children, pp. 196-203. 2021.}
        \resumeItemListEnd
        \resumeItemListStart
            \resumeItem{\textbf{[CHI Play 2021]} Derek Haqq, \textbf{Morva Saaty}, Jonathan T. Rukaj, Saylee Marulkar, Justin Israel, Emily Newton, Rudra Patel, Stephen Tan,  and D. Scott McCrickard. “Toward a Design Theory of Game-Mediated Social Experiences - A Study of Among Us.” In Proceedings of the Annual Symposium on Computer-Human Interaction in Play, 2021.}
        \resumeItemListEnd
         \vspace{-0.4cm}
        \resumeItemListStart
            \resumeItem{\textbf{[CHItaly 2021 - Nature HCI Workshop]} \textbf{Morva Saaty}, Derek Haqq, Stephen Dooley, Jerin Manalel, Sophia Pentakalos, Samridhi Roshan, Devin Toms, and D. Scott McCrickard. "Exergames and Nature." In Proceedings of the CEUR Workshop, 2901, pp. 8–15. 2021.}    
        \resumeItemListEnd
        \resumeItemListStart
            \resumeItem{\textbf{[CHItaly 2021 - Nature HCI Workshop]} Derek Haqq, \textbf{Morva Saaty}, and D. Scott McCrickard. "Re (Connecting) through Shared Remote Outdoor Play." In Proceedings of the CEUR Workshop, 2901, pp. 32–40. 2021.} 
        \resumeItemListEnd
        \vspace{-0.4cm}
        \resumeItemListStart
            \resumeItem{\textbf{[CHI 2020]} Lindah Kotut, Neelma Bhatti, \textbf{Morva Saaty}, Derek Haqq, Timothy L. Stelter and D. Scott McCrickard. “Clash of Times: Respectful Technology Space for Integrating Community Stories in Intangible Exhibits.” ACM CHI Conference on Human Factors in Computing Systems., Honolulu, HI. April 2020. [24.3\% Acceptance Rate]}
        \resumeItemListEnd

         % \resumeItemListStart
          %  \resumeItem{     
           %[CHI 2021] Morva Saaty, Mahmoud Reza Hashemi. "A Conceptual Audio-Visual Game Attention Model for Efficient Bitrate Allocation in Cloud Gaming". ACM CHI Conference on Human Factors in Computing Systems. (Submitted) }
          %\resumeItemListEnd 
    \resumeSubHeadingListEnd
    
  %------------- Development Experience --------------
\section{Development Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Undergraduate Thesis Project}{June. 2016 - Aug. 2016}
      {University of Tehran}{Tehran, Iran}
      \resumeItemListStart
        \resumeItem{Design and Implementation of the social network system which is focused on transporting the information and media between members, using Ruby on Rails, REST API}
    \resumeItemListEnd
    
    \resumeSubheading
      {Web Developer}{June. 2015 - Aug. 2015}
      {Mohandesin Moshaver Memari Va Mohit}{Tehran, Iran}
      \resumeItemListStart
        \resumeItem{Back-end and Front-end Web developer of the company’s website, using Ruby on Rails, HTML, CSS, JavaScript and jQuery}
    \resumeItemListEnd
 \resumeSubHeadingListEnd
 

    
   %-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (Postgres), JavaScript, HTML/CSS, R, Matlab} \\
    \textbf{Research Methods}{:surveys, interviewing, diary studies, focus groups, participant observation | Wireframing, Prototyping, Personas, Heuristic Evaluation  | Experimental Design, Statistical Hypothesis Testing}\\
     \textbf{Frameworks}{:Ruby on Rails, Windows Form Applications using C\#}\\
  %   \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     \textbf{Developer Tools}{: Git, Visual Studio, PyCharm, IntelliJ, Eclipse, Gephi, Tableau, Rstudio, Android Studio, Observable, Elastic Search, Figma} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, D3, PyTorch}
    }}
 \end{itemize}
%-----------Academic PROJECTS-----------
\section{Academic Projects}
    \resumeSubHeadingListStart
    
     \resumeProjectHeading
      {\textbf{Introduction to Deep Learning Course} $|$ \emph{Python, Pytorch}}{Jan. 2021 - May. 2021}
      \resumeItemListStart
        \resumeItem{Implementation of different CNN models for automatic detection of COVID-19 based of chest X-ray images.}
      \resumeItemListEnd 
          
     \resumeProjectHeading
          {\textbf{Information Visualization Course} $|$ \emph{D3.js, Tableau, Observable}}{Aug. 2020 - Dec. 2020}
          \resumeItemListStart
            \resumeItem{Design and implementation of the visualization related to Covid-19 and Air quality data.}
          \resumeItemListEnd 

         \resumeProjectHeading
          {\textbf{Introduction to Big Data} $|$ \emph{Docker, Elastic Search, Hadoop, Scala}}{Sep. 2017 - Jan. 2018}
          \resumeItemListStart
            \resumeItem{Designing and developing a reliable and scalabe system with specific features (Searching, Visualizing, and Distribution of nodes) }
          \resumeItemListEnd 
    
      \resumeProjectHeading
          {\textbf{Statistical Inference Course} $|$ \emph{R}}{Feb. 2017 - June. 2017}
          \resumeItemListStart
            \resumeItem{tatistical analysis of the real dataset from kaggle.com by using ANOVA table and calculating other parameters (such as power, p-value, ... )}
          \resumeItemListEnd 

      \resumeProjectHeading
          {\textbf{Pattern Recognition Course} $|$ \emph{Python, Matlab}}{Sep. 2016 - Jan. 2017}
          \resumeItemListStart
            \resumeItem{Design and Implementation of neural networks such as MLP and RBF, then train those for classification of the special given dataset.}
            \resumeItem{Implementation of clustering methods(such as KNN, Naïve Bayes, ...)}
          \resumeItemListEnd    
          
         \resumeProjectHeading
          {\textbf{Social Networks Course} $|$ \emph{Java, Gephi}}{Sep. 2016 - Jan. 2017}
          \resumeItemListStart
            \resumeItem{Implementation of graphs characteristics like betweenness centrality and clustering coefficiency on large graph.}
          \resumeItemListEnd 
          
     \resumeProjectHeading
          {\textbf{Internet Engineering Course} $|$ \emph{Ruby on Rails}}{Feb. 2015 - June. 2015}
          \resumeItemListStart
            \resumeItem{Design and Implementation of the FitNet website for the purpose of helping athletes to facilitate their exercise while using a device called "TotalCore."}
          \resumeItemListEnd 

     \resumeProjectHeading
          {\textbf{Artificial Intelligence Course} $|$ \emph{Python}}{Sep. 2014 - Jan. 2015}
          \resumeItemListStart
            \resumeItem{Implementation of Minimax algorithm with Alpha-Beta Pruning, Connect-four game}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{System Analysis and Design Course} $|$ \emph{C\#, Visual Studio}}{Feb. 2014 - June. 2014}
          \resumeItemListStart
            \resumeItem{Implementation of an email-based communication gateway for office of graduate studies, using Three-layered architecture and MVC pattern}
          \resumeItemListEnd 
          
    \resumeProjectHeading
          {\textbf{Computer Networks Course} $|$ \emph{C++, Socket Programming APIs}}{Feb. 2014 - June. 2014}
          \resumeItemListStart
            \resumeItem{Implementation of a document sharing network with emphasis on OSI protocol stack}
          \resumeItemListEnd           
          
  %   \resumeProjectHeading
   %       {\textbf{Operating System Course} $|$ \emph{C, C++}}{Sep. 2013 - Jan. 2014}
    %      \resumeItemListStart
     %       \resumeItem{Design and implementation of a multi-thread schema for memory management of a shared memory}            \resumeItem{Implementation of a CPU Scheduler}
      %    \resumeItemListEnd 
          
    \resumeProjectHeading
          {\textbf{Advanced Programming Course} $|$ \emph{C++, Socket Programming APIs}}{Feb. 2012 - June. 2012}
          \resumeItemListStart
            \resumeItem{Design and implementation of multithread social network application,(similar to Twitter)}
          \resumeItemListEnd 
          
           % \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
          %  \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
         %   \resumeItem{Visualized GitHub data to show collaboration}
        %    \resumeItem{Used Celery and Redis for asynchronous tasks}
       %   \resumeItemListEnd
      %\resumeProjectHeading
          %{\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
          %\resumeItemListStart
            %\resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
            %\resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
           % \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
           % \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
          %\resumeItemListEnd
    \resumeSubHeadingListEnd



%

%-----------PROGRAMMING SKILLS-----------



%-------------------------------------------

    
    %-----------Teaching Experience -----------
\section{Teaching Experience}
    \resumeSubHeadingListStart
    
     \resumeProjectHeading
        {\textbf{Graduate Teaching Assistant} $|$ \emph{Virginia Tech, Blacksburg, VA}}{}
          \resumeItemListStart
            \resumeItem{CS 5764: Information Visualization}{| Fall 2021}
            \resumeItem{CS 3724: Human Computer Introduction}{| Fall 2020}
            \resumeItem{CS 3724/5714: Introduction to Human Computer Interaction + Usability Engineering}{|  Two Semesters (Spring 2021, Summer 2021)}        
        \resumeItemListEnd 
        
     \resumeProjectHeading
        {\textbf{Graduate Teaching Assistant} $|$ \emph{University of Tehran, Tehran, Iran}}{}
          \resumeItemListStart
            \resumeItem{{Human-Computer Interaction Course}\emph{}} {|  Four semesters (Spring 2017, Fall 2017, Spring 2018, Fall 2019)}
            \resumeItem{Data Transmission Course} {| Fall 2017}  
            \resumeItem{Artificial Intelligence Course} {| Two Semesters (Spring 2017, Fall 2014)}  
        \resumeItemListEnd 
        
    \resumeSubHeadingListEnd



\end{document}
